A Theory of Bidirectional Type Synthesis for Simple Types

### 2023-07-20 tex/sec6-formalisation.tex
[ refactor ] Shorten soundness and completness

Induction proofs in our formalisation typically consist of three mutual definitions---one for the inductive type of derivations, one for a list of arguments, and one for an extension context.

@@

Then, the induction proof is nothing more than a function defined by pattern matching for each case: each constructor of bidirectional typing derivations is mapped to a corresponding constructor of typing derivations.
(The definition \ensuremath{\Varid{soundnessᵃ}} might be further removed if \Agda's termination checker 
The only (slightly) interesting case $\ChkRule{Sub}$ is proved by disregarding the identity proof \ensuremath{\Varid{refl}} and use the induction hypothesis (\ensuremath{\Varid{soundness}\;\Varid{t}}) directly:

>>>>

Our formal induction proofs typically consist of mutual definitions for the inductive type of derivations, for a list of arguments, for an extension context, and sometimes for an operation separately.

@@

The induction proof is nothing more than a function defined by pattern matching for each case: each constructor of bidirectional typing derivations is mapped to a corresponding constructor of typing derivations.
The only (slightly) interesting case $\ChkRule{Sub}$ is proved by disregarding the identity proof \ensuremath{\Varid{refl}} and use the induction hypothesis \ensuremath{\Varid{soundness}\;\Varid{t}} directly:
